### 2018-10-12 tex/abstract.tex
v1.3.2

In large-scale data-parallel analytics, \textit{shuffle}, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large network transfer overhead.
Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs). 
By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process. Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

>>>>

In large-scale data-parallel analytics, \textit{shuffle}, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large network transfer overhead.
Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs). 
{\color{blue}
During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
FRQ model displays utilization of resources in time dimension and calculate exectuion time of computing jobs on different DAG frameworks. 
We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
}
By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process. Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

### 2018-10-12 tex/conclusion.tex
v1.3.2

\section{Conclusion}
 In this paper, we present SCache, a cross-framework open source shuffle optimization system for DAG computing frameworks. SCache decouples the shuffle from computing pipeline and leverages shuffle data pre-fetching to mitigate the I/O overhead of the whole system. By scheduling tasks with application context, SCache bridges the gap among computing stages. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
 {\color{blue}
 At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Out evaluation result shows that SCache can provide a promising speedup to the DAG framework.
 }
 We believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks.

>>>>

\section{Conclusion}
 In this paper, we present SCache, a cross-framework open source shuffle optimization system for DAG computing frameworks. SCache decouples the shuffle from computing pipeline and leverages shuffle data pre-fetching to mitigate the I/O overhead of the whole system. By scheduling tasks with application context, SCache bridges the gap among computing stages. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
 {\color{blue}
 At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Our evaluation result shows that SCache can provide a promising speedup to the DAG framework. 
 Furthermore, we propose \textit{Framework Resources Quantification}(FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last we use FRQ model to verify SCache shuffle optimization by mathematics.
 Therefore we believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks. 
 }

### 2018-10-12 tex/evaluation.tex
v1.3.2

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
First we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.

@@

\subsection{Terasort}
We also evaluate Terasort \cite{spark-tera} --- a recognized shuffle intensive benchmark for distributed system analysis.
Terasort consists of two consecutive shuffles. The first shuffle reads the input data and uses a customized hash partition function for re-partitioning. The second shuffle partitions the data through a range partitioner. As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.

@@

\subsection{Production Workload}
We also evaluate some shuffle heavy queries from TPC-DS \cite{tpcds}. TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query number, and the vertical axis is query completion time. Spark with SCache outperforms the original Spark in almost all the queries. Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. The overall reduction portion of query time that SCache achieved is 40\% on average. Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera}
% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
% 		\label{fig:terasort}
% 	\end{subfigure}
% 	\vspace{0.08cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
% 		\label{fig:terashuffle}
% 	\end{subfigure}
% 	\caption{Terasort Evaluation}
% \end{figure}
\subsection{Overhead of Sampling}
In this part, we evaluate the overhead of sampling with different input data sizes on one node and cluster scales. In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node. But it remains relatively stable when the cluster size scales up. It makes SCache a scalable system in cluster.

>>>>

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
First we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.

@@

\subsection{Terasort}
We also evaluate Terasort --- a recognized shuffle intensive benchmark for distributed system analysis.
Terasort consists of two consecutive shuffles. The first shuffle reads the input data and uses a customized hash partition function for re-partitioning. The second shuffle partitions the data through a range partitioner. As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.

@@

\subsection{Production Workload}
We also evaluate some shuffle heavy queries from TPC-DS. TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query number, and the vertical axis is query completion time. Spark with SCache outperforms the original Spark in almost all the queries. Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. The overall reduction portion of query time that SCache achieved is 40\% on average. Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera}
% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
% 		\label{fig:terasort}
% 	\end{subfigure}
% 	\vspace{0.08cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
% 		\label{fig:terashuffle}
% 	\end{subfigure}
% 	\caption{Terasort Evaluation}
% \end{figure}
\subsection{Overhead of Sampling}
In this part, we evaluate the overhead of sampling with different input data sizes on one node and cluster scales. In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node. But it remains relatively stable when the cluster size scales up. It makes SCache a scalable system in cluster.

### 2018-10-12 tex/intro.tex
v1.3.2

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after all the data from its ancestor stage by default. As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier such as \textit{early start} from Apache Hadoop \cite{hadoop}. However, such early start is by no means a panacea. This is because although the reduce tasks can start fetching data earlier, the computation can only take place after all the data is ready. Since each phase receives a fixed bundle of resources, starting a reduce task early always introduces an unnecessary early allocation of slot.

@@

{\color{blue}
In order to visually describe above-mentioned resources scheduling and analyze deficiencies, we propose \textit{Framework Resources Quantification}(FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to help us analyze the deficiencies of resources scheduling and optimize it.
}

Can we efficiently optimize the data shuffling without significantly changing every framework?
In this paper, we answer this question in the affirmative with S(huffle)Cache, an opne source plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle read and write from both map and reduce tasks.
Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
In addition, SCache pre-schedules the reduce tasks and pre-fetches the shuffle data to the location of the reduce tasks without launching them.
Such pre-scheduling and pre-fetching effectively desynchronize the network I/O operation, while avoiding the waste of computational resources compared to the early start mechanism.
%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks. SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks. In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch. In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a mathematic model called \textit{Framework Resources Quantification}(FRQ) model. We use FRQ model to analyze the principle of SCache and calculate the time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}

>>>>

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after all the data from its ancestor stage by default. As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier such as \textit{early start} from Apache Hadoop\footnote{http://hadoop.apache.com/}. However, such early start is by no means a panacea. This is because although the reduce tasks can start fetching data earlier, the computation can only take place after all the data is ready. Since each phase receives a fixed bundle of resources, starting a reduce task early always introduces an unnecessary early allocation of slot.

@@

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delay the execution time of reduce phase. 
This situation will be amplified in shuffle-sensitive tasks.
}

Can we efficiently optimize the data shuffling without significantly changing every framework?
In this paper, we answer this question in the affirmative with S(huffle)Cache, an opne source plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.

Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle read and write from both map and reduce tasks.
Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
In addition, SCache pre-schedules the reduce tasks and pre-fetches the shuffle data to the location of the reduce tasks without launching them.
Such pre-scheduling and pre-fetching effectively desynchronize the network I/O operation, while avoiding the waste of computational resources compared to the early start mechanism.
%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks. SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks. In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch. In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model. We use FRQ model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}

### 2018-10-12 tex/model.tex
Complete model caption.
Version 1.1.
v1.3.2

\subsection{The FRQ Model}\label{model_overview}
The current distributed parallel computing frameworks mostly use DAG(Directed acyclic graph) to describe computation logic. A shuffle phase is required between each adjacent DAG computation phase. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose FRQ model. After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce FRQ model by taking a simple MapReduce as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
\begin{itemize}
	\item Input Data Size\((D)\): The data size of the computation phase.
	\item Data Conversion Rate\((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
    \item Computation Round Number\((N)\): The number of rounds needed to complete the computation phase using the current computation resources. The number of rounds depends on the current computation resources and the settings of the computation job. Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the Map phase consists of 200 map tasks. Then we need 4 rounds of computation to complete the Map phase.
    \item Computation Speed\((V_{i})\): 
    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed\((V_{Shuffle})\): 
    Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
\end{itemize}

@@

Table \ref{table2} shows the calculational results of FRQ model in Amazon EC2 environment. \(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices. We also set K to the same empirical value. The formulas in the table are all the same except \(T_{P\_Shuffle}\). In this environment, Terasort on Hadoop Mapreduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. In the case of Legacy, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_net1}
				\caption{\color{blue}}
				\label{fig:hadoop_net1}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_net2}
				\caption{\color{blue}}
				\label{fig:hadoop_net2}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}FRQ Model With SCache}
		\label{fig:hadoop_net}
	\end{minipage}
\end{figure}

>>>>

\subsection{The FRQ Model}\label{model_overview}
The current distributed parallel computing frameworks mostly use \textit{Directed acyclic graphs}(DAGs) to describe computation logic. A shuffle phase is required between each adjacent DAG computation phase. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose FRQ model. After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce FRQ model by taking a simple MapReduce as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
\begin{enumerate}
	\item Input Data Size\((D)\): The data size of the computation phase.
	\item Data Conversion Rate\((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
    \item Computation Round Number\((N)\): The number of rounds needed to complete the computation phase using the current computation resources. The number of rounds depends on the current computation resources and the settings of the computation job. Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the Map phase consists of 200 map tasks. Then we need 4 rounds of computation to complete the Map phase.
    \item Computation Speed\((V_{i})\): 
    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed\((V_{Shuffle})\): 
    Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
\end{enumerate}

@@

Table \ref{table2} shows the calculational results of FRQ model in Amazon EC2 environment. \(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices. We also set K to the same empirical value. The formulas in the table are all the same except \(T_{P\_Shuffle}\). In this environment, Terasort on Hadoop Mapreduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. In the previous case, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_net1}
				\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
				\label{fig:hadoop_net1}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_net2}
				\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
				\label{fig:hadoop_net2}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}Network utilization on Hadoop Mapreduce with SCache}
		\label{fig:hadoop_net}
	\end{minipage}
\end{figure}

### 2018-10-12 tex/relatedwork.tex
v1.3.2

{\color{blue}
\textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel}(BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on(Hadoop Madpreduce can also be considered as a special case of only one superstep in BSP model). 
In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
Inspired by \cite{verma2011aria}, \cite{herodotou2011hadoop}, and \cite{polo2010performance}, we present \textit{Framework Resources Quantification}(FRQ) model to describe the performance of DAG frameworks.
In \cite{verma2011aria}, the author designs a model and divides execution into three parts: Map, Shuffle and Reduce. And then the author uses a greedy algorithm to roughly calculate the max, min and mean execution time of Map and Reduce phases.
In \cite{herodotou2011hadoop}, the author presents a detailed set of mathematical performance models for describing the execution of a MapReduce job. The execution is seperated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. The performance models describe each above-mentioned phases and combine into a overall Mapreduce job model. 
However, none of the above models meet our requirements for analyzing shuffle.
The model in \cite{verma2011aria} is not able to accurately describe the overhead caused by shuffle under different scheduling strategies. The model in \cite{herodotou2011hadoop} calculates overhead of various phases including shuffle, but most of them are redundant. 
Different from these models, our FRQ model quantifies computing and I/O resources and displays them in time dimension. FRQ model focuses on describing the overhead caused by shuffle in different scheduling strategies, which satisfy our demand.
}

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce \cite{hadoop} is the most classic approach to handle shuffle overhead. Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, map and reduce slot ratio, etc). DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage to decrease the time of waiting for outputs of map tasks. All of them left the explicit I/O time in an occupied computation slot. Instead, SCache can start shuffle pre-fetching without consuming slots. iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages, in order to start fetching data from previous stage earlier. But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing by combining DAG information and heuristic algorithms.

>>>>

{\color{blue}
\textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel}(BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on(Apache Hadoop Madpreduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model). 
In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
Inspired by \cite{verma2011aria}, \cite{herodotou2011hadoop}, and \cite{polo2010performance}, we present \textit{Framework Resources Quantification}(FRQ) model to describe the performance of DAG frameworks.
In \cite{verma2011aria}, the author designs a model and divides execution into three parts: Map, Shuffle and Reduce. And then the author uses a greedy algorithm to roughly calculate the max, min and mean execution time of Map and Reduce phases.
In \cite{herodotou2011hadoop}, the author presents a detailed set of mathematical performance models for describing the execution of a MapReduce job. The execution is seperated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. The performance models describe each above-mentioned phases and combine into a overall Mapreduce job model. 
However, none of the above models meet our requirements for analyzing shuffle.
The model in \cite{verma2011aria} is not able to accurately describe the overhead caused by shuffle under different scheduling strategies. The model in \cite{herodotou2011hadoop} calculates overhead of various phases including shuffle, but most of them are redundant. 
Different from these models, our FRQ model quantifies computing and I/O resources and displays them in time dimension. FRQ model focuses on describing the overhead caused by shuffle in different scheduling strategies, which satisfy our demand.
}

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is the most classic approach to handle shuffle overhead. Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, map and reduce slot ratio, etc). DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage to decrease the time of waiting for outputs of map tasks. All of them left the explicit I/O time in an occupied computation slot. Instead, SCache can start shuffle pre-fetching without consuming slots. iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages, in order to start fetching data from previous stage earlier. But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing by combining DAG information and heuristic algorithms.
